Stage-structured evolutionary demography for simultaneous hermaphrodites with partial selfing

### 2020-09-29 notes/notes-SA-partSelf-wDemography.tex
Fixed equations in the last section of the notes (where how-you-are-produced does not effect your demographic rates). Fixed equations in matlab files, wrote code to efficiently search for coexistence area by titrating (halving distance to threshold at each step) :) Next step: use same titrate method to determine extinction.

% Packages from Am. Nat. Template
\usepackage[sc]{mathpazo} %Like Palatino with extensive math support
\usepackage{fullpage}
\usepackage[authoryear,sectionbib,sort]{natbib}
\linespread{1.15}
\usepackage[utf8]{inputenc}
\usepackage{lineno}

@@

The coexistence conditions become:
\begin{equation} \label{eq:coexist_bigAA}
	\lambda_{AA} < 
			\rho\left(\begin{array}{cc}
\mathbf{U}_{Aa} + \frac{1}{2} (1 - \delta C_{Aa}) \mbf{F}_{Aa} +\frac{1}{2} (1 - C_{AA})\frac{\mbf{F}_{AA}\hat{\mbf{p}}_{AA}\otimes \mathbf{1}^\tr_{\omega} \mathbf{F}_{Aa}^\prime}{\mathbf{1}^\tr_\omega \mathbf{F}_{AA}^\prime \hat{\mathbf{p}}_{AA}	} & (1-C_{aa}) \mbf{F}_{aa} \\
\frac{1}{4} C_{Aa} (1 - \delta) \mbf{F}_{Aa}  &\mathbf{U}_{aa} +C_{aa} (1 - \delta) \mbf{F}_{aa}  \\ 
			\end{array} \right), \\ 
\end{equation}

\begin{equation} \label{eq:coexist_baa}
	\lambda_{AA} < 
			\rho\left(\begin{array}{cc}
\mathbf{U}_{Aa} + \frac{1}{2} (1 - \delta C_{Aa}) \mbf{F}_{Aa} +\frac{1}{2} (1 - C_{aa})\frac{\mbf{F}_{aa}\hat{\mbf{p}}_{aa}\otimes \mathbf{1}^\tr_{\omega} \mathbf{F}_{Aa}^\prime}{\mathbf{1}^\tr_\omega \mathbf{F}_{aa}^\prime \hat{\mathbf{p}}_{aa}	} & (1-C_{AA}) \mbf{F}_{AA} \\
\frac{1}{4} C_{Aa} (1 - \delta) \mbf{F}_{Aa}  &\mathbf{U}_{AA} +C_{AA} (1 - \delta) \mbf{F}_{AA}  \\ 
			\end{array} \right), \\ 
\end{equation}

@@

\begin{eqnarray} \label{eq:coexist_AA}
\lambda_{AA}> 
			\rho\left(
					\begin{array}{cc|cc}
						\sigma_{Aa}(1 - \gamma_{Aa}) &  \frac{1}{2} (1 - \delta C_{Aa}) f_{Aa} +\frac{1}{2} (1 - C_{AA})\frac{f^\prime_{Aa}f_{AA}}{f^\prime_{AA}} &0 & (1-C_{aa})f_{aa}\\
						\sigma_{Aa} \gamma_{Aa}     & s_{Aa}& 0 & 0\\ \hline
							0 & \frac{1}{4}C_{Aa}(1-\delta)f_{Aa} &\sigma_{aa}(1 - \gamma_{aa})  & C_{aa}(1-\delta)f_{aa}\\
								0 & 0 & \sigma_{aa} \gamma_{aa}     & s_{aa}
					\end{array}
				\right). 
\end{eqnarray}

>>>>

% Packages from Am. Nat. Template
\usepackage[sc]{mathpazo} %Like Palatino with extensive math support
\usepackage{fullpage}
\usepackage[authoryear,sectionbib,sort] {natbib}
\linespread{1.15}
\usepackage[utf8]{inputenc}
\usepackage{lineno}

@@

The coexistence conditions become:
\begin{equation} \label{eq:coexist_bigAA}
	\lambda_{AA} < 
			\rho\left(\begin{array}{cc}
\mathbf{U}_{Aa} + \frac{1}{2} (1 - \delta C_{Aa}) \mbf{F}_{Aa} +\frac{1}{2} (1 - C_{AA})\frac{\mbf{F}_{AA}\hat{\mbf{p}}_{AA}\otimes \mathbf{1}^\tr_{\omega} \mathbf{F}_{Aa}^\prime}{\mathbf{1}^\tr_\omega \mathbf{F}_{AA}^\prime \hat{\mathbf{p}}_{AA}	} & (1-C_{aa}) \mbf{F}_{aa}+ (1 - C_{AA})\frac{\mbf{F}_{AA}\hat{\mbf{p}}_{AA}\otimes \mathbf{1}^\tr_{\omega} \mathbf{F}_{aa}^\prime}{\mathbf{1}^\tr_\omega \mathbf{F}_{AA}^\prime \hat{\mathbf{p}}_{AA}	}  \\
\frac{1}{4} C_{Aa} (1 - \delta) \mbf{F}_{Aa}  &\mathbf{U}_{aa} +C_{aa} (1 - \delta) \mbf{F}_{aa}  \\ 
			\end{array} \right), \\ 
\end{equation}

\begin{equation} \label{eq:coexist_baa}
	\lambda_{AA} < 
			\rho\left(\begin{array}{cc}
\mathbf{U}_{Aa} + \frac{1}{2} (1 - \delta C_{Aa}) \mbf{F}_{Aa} +\frac{1}{2} (1 - C_{aa})\frac{\mbf{F}_{aa}\hat{\mbf{p}}_{aa}\otimes \mathbf{1}^\tr_{\omega} \mathbf{F}_{Aa}^\prime}{\mathbf{1}^\tr_\omega \mathbf{F}_{aa}^\prime \hat{\mathbf{p}}_{aa}	} & (1-C_{AA}) \mbf{F}_{AA}+\ (1 - C_{aa})\frac{\mbf{F}_{aa}\hat{\mbf{p}}_{aa}\otimes \mathbf{1}^\tr_{\omega} \mathbf{F}_{AA}^\prime}{\mathbf{1}^\tr_\omega \mathbf{F}_{aa}^\prime \hat{\mathbf{p}}_{aa}	} \\
\frac{1}{4} C_{Aa} (1 - \delta) \mbf{F}_{Aa}  &\mathbf{U}_{AA} +C_{AA} (1 - \delta) \mbf{F}_{AA}  \\ 
			\end{array} \right), \\ 
\end{equation}

@@

\begin{eqnarray} \label{eq:coexist_AA}
\lambda_{AA}> 
			\rho\left(
					\begin{array}{cc|cc}
						\sigma_{Aa}(1 - \gamma_{Aa}) &  \frac{1}{2} (1 - \delta C_{Aa}) f_{Aa} +\frac{1}{2} (1 - C_{AA})\frac{f^\prime_{Aa}f_{AA}}{f^\prime_{AA}} &0 & (1-C_{aa})f_{aa}+ (1 - C_{AA})\frac{f^\prime_{aa}f_{AA}}{f^\prime_{AA}}\\
						\sigma_{Aa} \gamma_{Aa}     & s_{Aa}& 0 & 0\\ \hline
							0 & \frac{1}{4}C_{Aa}(1-\delta)f_{Aa} &\sigma_{aa}(1 - \gamma_{aa})  & C_{aa}(1-\delta)f_{aa}\\
								0 & 0 & \sigma_{aa} \gamma_{aa}     & s_{aa}
					\end{array}
				\right). 
\end{eqnarray}
